HiC Contact Map Comaprison Using Graphlet Approach

### 2018-03-29 papers/manuscripts/manuscript.tex
added t-test table
Coverted the correlation image to latex

\documentclass[a4,center,fleqn]{NAR}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}
% Enter dates of publication
\copyrightyear{2017}
\pubdate{18 March 2017}
\pubyear{2017}
\jvolume{37}
\jissue{12}

@@

We have conducted one-sided
t-test in order to test whether the average correlations across
contact maps is equal to 1  and whether the average 
correlations across orbits is equal to 1. The results
for both test showed that all values are significantly less than 1.
Please refer to supplementary material for result of the 
full list of t-test results.

\newpage
\section{Resources}
\textbf{Hi-C Datasets:}
\begin{enumerate}
    \item \href{https://github.com/rasoolianbehnam/watson}{Code base for this article}
    \item \href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
        {Datasets including cancerous cells}
    \item \href{https://bcm.app.box.com/v/aidenlab/folder/11234760671}{Original Datasets}
\end{enumerate}

%\begin{tikzpicture}
%    \node [] (a) at (0, 0) {
%        $\begin{pmatrix}  
%            C_{\scriptscriptstyle 1,1,1,1}     &   C_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C_{\scriptscriptstyle 1,1,1,N_1} \\
%            C_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
%            \vdots                             &                & \ddots           &      \\
%            C_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C_{\scriptscriptstyle 1,1,N_1, N_1} 
%        \end{pmatrix}$
%    };
%    \node [] (b) [left=1pt of a] {$N_1$};
%    \node [] (c) [above=1pt of a] {$N_1$};
%\end{tikzpicture}
\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}

>>>>

\documentclass[a4,center,fleqn]{NAR}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[super]{nth}
\usepackage{multirow}
% Enter dates of publication
\copyrightyear{2017}
\pubdate{18 March 2017}
\pubyear{2017}
\jvolume{37}
\jissue{12}

@@

We have conducted one-sided
t-test in order to test whether the average correlations across
contact maps is equal to 1  and whether the average 
correlations across orbits is equal to 1. The results
for both test showed that all values are significantly less than 1.
Please refer to supplementary material for result of the 
full list of t-test results.
\begin{table}[]
    \centering
    \resizebox{.5\textwidth}{!}{
    \begin{tabular}{l|ccccccc}
        \rule{0pt}{25pt}
                  & One       & MIT-RL       & ALL-RL       & ALL-MIT      & ALL-CALL4    & CALL4-MIT    & CALL4-RL     \\ \hline
        \rule{0pt}{25pt}
        One       & -         & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater & \textgreater \\
        \rule{0pt}{25pt}
        MIT-RL    & \textless & -            & \textless    & \textless    & \textless    & \textless    & \textless    \\
        \rule{0pt}{25pt}
        ALL-RL    & \textless & \textgreater & -            & \textless    & \textless    & \textless    & \textless    \\
        \rule{0pt}{25pt}
        ALL-MIT   & \textless & \textgreater & \textgreater & -            & =            & =            & =            \\
        \rule{0pt}{25pt}
        ALL-CALL4 & \textless & \textgreater & \textgreater & =            & -            & =            & =            \\
        \rule{0pt}{25pt}
        CALL4-MIT & \textless & \textgreater & \textgreater & =            & =            & -            &              \\
        CALL4-RL  & \textless & \textgreater & =            & =            & =            & =            & -           
        \rule{0pt}{25pt}
    \end{tabular}}
    \caption{}
    \label{tab:t-test}
\end{table}
\newpage
\section{Resources}
\textbf{Hi-C Datasets:}
\begin{enumerate}
    \item \href{https://github.com/rasoolianbehnam/watson}{Code base for this article}
    \item \href{http://sysbio.rnet.missouri.edu/T0510/tmp_download/link_to_download_genome_data/}
        {Datasets including cancerous cells}
    \item \href{https://bcm.app.box.com/v/aidenlab/folder/11234760671}{Original Datasets}
\end{enumerate}

\tikzset{
    myArrow/.style={
    single arrow,
    draw,
    text width =.3cm,
    scale=.8,
    shade, shading=axis, left color=orange, right color=yellow,
    shading angle=45,
    blur shadow={shadow blur steps=5,shadow blur extra rounding=1.3pt}
    }
}

\begin{table}[]
    \centering
    \resizebox{.5\textwidth}{!}{
        \begin{tabular}{lllllp{1cm}ll}
            &\multicolumn{1}{c}{\textbf{\huge Cell A graphlets $S^A_{i,j}$}}  & \multicolumn{1}{c}{\textbf{\huge Cell B graphlets $S^B_{i,j}$}} 
            && \multicolumn{1}{c}{\textbf{\huge Correlation Vector $m^{A,B}_{i,j}$}} 
            && \multicolumn{1}{c}{\textbf{\huge Correlation Matrix $M^{A,B}_{i,j}$}} \vspace{.5cm} \\
        &\multicolumn{1}{c}{$N_1$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
        \rule{0pt}{40pt}
        $N_1$ &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 1,1,1,1}     &   C^A_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,1,1,N_1} \\
            C^A_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,1,N_1, N_1} 
        \end{pmatrix}$} &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 1,1,1,1}     &   C^B_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,1,1,N_1} \\
            C^B_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^B_{\scriptscriptstyle 1,1,N_1, N_1} 
        \end{pmatrix}$} &
        \begin{tikzpicture}
            \draw [->] (0, 0) -> (2, 0);
        \end{tikzpicture} &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72}
        \end{pmatrix}$} \vspace{1cm}\\

        &\multicolumn{1}{c}{$N_2$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
        \rule{0pt}{45pt}
        $N_1$ &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 1,2,1,1}     &   C^A_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,2,1,N_1} \\
            C^A_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 1,2,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,2,N_1, N_1} 
        \end{pmatrix}$}&
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 1,2,1,1}     &   C^B_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,2,1,N_2} \\
            C^B_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 1,2,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 1,2,N_1, N_2} 
        \end{pmatrix}$}&
        \begin{tikzpicture}
            \draw [->] (0, 0) -> (2, 0);
        \end{tikzpicture} &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72}
        \end{pmatrix}$} \vspace{1cm}\\

        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} \vspace{1cm}\\
        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} 
        &&\resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72} \\ 
            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72} \\ 
            \vdots & \vdots & \vdots \\
            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72} \\ 
            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
        \end{pmatrix}$} \vspace{1cm}\\

        &\multicolumn{1}{c}{\Large o}  & \multicolumn{1}{c}{\Large o} && \multicolumn{1}{c}{\Large o} \vspace{1cm}\\

        &\multicolumn{1}{c}{$N_{23}$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
        \rule{0pt}{45pt}
        $N_{22}$ &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
        \end{pmatrix}$}&
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
        \end{pmatrix}$}&
        \begin{tikzpicture}
            \draw [->] (0, 0) -> (2, 0);
        \end{tikzpicture} &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
        \end{pmatrix}$} \vspace{1cm}\\

        &\multicolumn{1}{c}{$N_{23}$}  & \multicolumn{1}{c}{72} && \multicolumn{1}{c}{72} \vspace{.5cm}\\
        \rule{0pt}{45pt}
        $N_{23}$ &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
        \end{pmatrix}$}&
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
        \end{pmatrix}$}&
        \begin{tikzpicture}
            \draw [->] (0, 0) -> (2, 0);
        \end{tikzpicture} &
        \resizebox{\linewidth}{!}{%
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
        \end{pmatrix}$}\vspace{1cm}

    \end{tabular}}
    \caption{}
    \label{tab:t-test}
\end{table}

\resizebox{.5\textwidth}{!}{
\begin{tikzpicture}
    %First row
    %first
    \node [] (a1) at (0, 0) {
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 1,1,1,1}     &   C^A_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,1,1,N_1} \\
            C^A_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,1,N_1, N_1} 
        \end{pmatrix}$
    };
    \node [] (h11) [left=1pt of a1] {$N_1$};
    \node [] (w11) [above=1pt of a1] {$N_1$};

    %second
    \node [] (b1) [right = 1cm of a1] {
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 1,1,1,1}     &   C^B_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,1,1,N_1} \\
            C^B_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C^B_{\scriptscriptstyle 1,1,N_1, N_1} 
        \end{pmatrix}$
    };
    \node [] (h12) [left=1pt of b1] {$N_1$};
    \node [] (w12) [above=1pt of b1] {$73$};

    %third
    \node [] (c1) [right = 1cm of b1] {
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 1,1,0}     &   m_{\scriptscriptstyle 1,1,1}  & \cdots    &    m_{\scriptscriptstyle 1,1,72}
        \end{pmatrix}$
    };
    \node [] (w3) [above=1pt of b1] {$73$};
    \draw [->] (b1.east) to (c1.west);

    %Second Row
    %first
    \node [] (a2) [below=1cm of a1] {
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 1,2,1,1}     &   C^A_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 1,2,1,N_1} \\
            C^A_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 1,2,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 1,2,N_1, N_1} 
        \end{pmatrix}$
    };
    \node [] (h21) [left=1pt of a2] {$N_1$};
    \node [] (w21) [above=1pt of a2] {$N_2$};

    %second
    \node [] (b2) [right = 1cm of a2] {
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 1,2,1,1}     &   C^B_{\scriptscriptstyle 1,2,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 1,2,1,N_2} \\
            C^B_{\scriptscriptstyle 1,2,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 1,2,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 1,2,N_1, N_2} 
        \end{pmatrix}$
    };
    \node [] (h22) [left=-.2cm of b2] {$\scriptstyle N_1 + N_2$};
    \node [] (w22) [above=1pt of b2] {$73$};

    %third
    \node [] (c2) [right = 1cm of b2] {
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 1,2,0}     &   m_{\scriptscriptstyle 1,2,1}  & \cdots    &    m_{\scriptscriptstyle 1,2,72}
        \end{pmatrix}$
    };
    \node [] (w3) [above=1pt of b2] {$73$};
    \draw [->] (b1.east) to (c1.west);

    \node [] (transition) [below=1cm of a2] {};

    %Second Row
    %first
    \node [] (a3) [below=1cm of transition] {
        $\begin{pmatrix}  
            C^A_{\scriptscriptstyle 22,23,1,1}     &   C^A_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^A_{\scriptscriptstyle 22,23,1,N_1} \\
            C^A_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^A_{\scriptscriptstyle 22,23,N_1,1}   &                &                  &    C^A_{\scriptscriptstyle 22,23,N_1, N_1} 
        \end{pmatrix}$
    };
    \node [] (h31) [left=1pt of a3] {$N_1$};
    \node [] (w31) [above=1pt of a3] {$N_2$};

    \node [] (transition) [] {};

    %second
    \node [] (b3) [right = 1cm of a3] {
        $\begin{pmatrix}  
            C^B_{\scriptscriptstyle 22,23,1,1}     &   C^B_{\scriptscriptstyle 22,23,1,1}  & \cdots    &    C^B_{\scriptscriptstyle 22,23,1,N_2} \\
            C^B_{\scriptscriptstyle 22,23,2,1}     &                &                  &      \\
            \vdots                             &                & \ddots           &      \\
            C^B_{\scriptscriptstyle 22,23,N_2,1}   &                &                  &    C^B_{\scriptscriptstyle 22,23,N_1, N_2} 
        \end{pmatrix}$
    };
    \node [] (h32) [left=-.2cm of b3] {$\scriptstyle N_1 + N_2$};
    \node [] (w32) [above=1pt of b3] {$73$};

    %third
    \node [] (c3) [right = 1cm of b3] {
        $\begin{pmatrix}  
            m_{\scriptscriptstyle 22,23,0}     &   m_{\scriptscriptstyle 22,23,1}  & \cdots    &    m_{\scriptscriptstyle 22,23,72}
        \end{pmatrix}$
    };
    \node [] (w3) [above=1pt of b3] {$73$};
    \draw [->] (b1.east) to (c1.west);

\end{tikzpicture}}
\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}
